\chapter{Conclusion}
\label{Conclusion}
%
The conclusion provided in this chapter serves as an answer to the research question in \autoref{ResearchQuestion} which is:

\begin{quote}
	\textbf{\textit{How can methods for a human-centered design approach be applied in the design process of the TonePrint Community?}}
\end{quote}

The design process of the TonePrint app were analyzed based on a interview with TC. Through this it was found that the SCRUM framework is an important aspect of the design process which have to be taken into account when looking at how methods may be applied. Furthermore it's found that the design process is base on little to non focus on the user, which means that there is no previous experience to consider when suggesting methods for the design process. A conceptual model of the TonePrint community were derived from the interview and is used as base when planing the design process process of the TonePrint community.\\
In order to make methods for a human-centered design approach relatable for the design process of the TonePrint community, five tasks is suggested (See \autoref{TaskAndMethods}). The proposed tasks approaches different aspects of the TonePrint community, in which methods for human-centered design is considered beneficial.\\
Task 1 focus on designing the information architecture of the TonePrint community. For this it's proposed to conduct a participatory design workshop in order to explore the users mental model. Another proposal is to conduct prototype tests, evaluating different design approaches. Task 2 focus on the developing the Tag feature of the TonePrint community, in order make it apprehensible for the users. It's proposed to conduct a descriptive analysis in order to explore how subjective sensory attributes may be transformed into apprehensible tags, used for categorizing a TonePrint. Task 3 focus on the extend of which self-promoting functionalities should be included in the TonePrint community. It's proposed to conduct a exploratory study of other platforms used for sharing self created music presets. Task 4 focus on testing different designs of the GUI of the app. It's proposed to conduct an A/B test of different design suggestions for the GUI. Task 5 focus on defining the user groups of the TonePrint community. It's proposed to address this by creating personas that represents the users, which might help aiming the focus towards the user in future design tasks. \\
\\
A user study was conducted based on the participatory design approach proposed in task 1. The user study featured a card sort experiment and a user workshop resulting in a conceptualized version of the users mental model of the TonePrint community, to the extend of the task provided in the workshop (see \autoref{fig:ConcludingModel}).